Why do we Eval?\\\Large A large-scale study of Eval usage in R

### 2021-03-30 paper/main.tex
Package environment

We observe that a disproportionately high number of core R \eval calls
access the caller's caller's environment. This is because many core R
functions call functions that pass the result of \c{parent.frame()} to
an \eval. A disproportionately high number of calls to \eval happens
in an extended top-level environment. This can be explained by the
fact that many packages evaluate code passed from the user's workspace
in the top-level environment to access the bindings.

@@

>>>>

We observe that a disproportionately high number of core R \eval calls
access the  caller's environment. This is because many core R
functions call functions that pass the result of \c{parent.frame()} to
an \eval. A disproportionately high number of calls to \eval happens
in an extended top-level environment. This can be explained by the
fact that many packages evaluate code passed from the user's workspace
in the top-level environment to access the bindings.

@@

\paragraph{Touching package environments.} It refers to the \emph{namespace} of a package. A call to \c{library(packageName)}, which load libraries in R, for instance, will populate environment \c{package:packageName}. It is a \emph{base} function though, so we do not see it in the CRAN dataset. However, R still makes it possible to access any package environments and \packageNbPackageEnvSites call sites, \ie \packagePackageEnvSitePercent access a package environment, from \packageNbPackageEnvPackages different packages. Those packages perform introspection, to represent and search any environment by name, in package \emph{envnames}, to containerize tests, as with \emph{testthat} and \emph{unitizer}, to create a custom OOP system with \emph{R.oo}, or to create poor man's hidden functions in \emph{USSCXenaTools}.

It is also used to implement a custom caching mechanism in packages \emph{g.data} and \emph{SOAR}.
